Ordinal bhsdtr tutorial

### 2020-02-17 ordinal/ordinal.Rmd
ordinal github markdown readme

```{r init, include=F,echo=F}
knitr::opts_chunk$set(dev = 'svg', comment = NA, fig.path='Figs/',fig.width=8, fig.height=6,
                      echo=TRUE, warning = FALSE, error = FALSE, message = FALSE,
                      cache.path = '~/windows/temp/ordinal', cache=T)

@@

The thresholds are determined by the items, by the properties of the
participants, and by the context in which the measurement takes
place. The assumption that important latent aspects of the process of
psychological measurement are constant across participants is so
ridiculous it should be laughed at on the street.

>>>>

---
title: "Ordinal bhsdtr tutorial"
output:
  md_document:
    variant: markdown_github
---
```{r init, include=F,echo=F}
knitr::opts_chunk$set(dev = 'svg', comment = NA, fig.path='Figs/',fig.width=8, fig.height=6,
                      echo=TRUE, warning = FALSE, error = FALSE, message = FALSE,
                      cache.path = '~/windows/temp/ordinal/', cache=T)

@@

The thresholds are determined by the items, by the properties of the
participants, and by the context in which the measurement takes
place. The assumption that an important latent aspect of the process
of psychological measurement is constant across participants is so
ridiculous it should be laughed at on the street.
